Manuscript 2: Child Health Outcomes

### 2021-10-05 papertwo_child_health.Rmd
Minor change to correct issue with subsetting.

effects_mat2$lower <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Lower,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Lower)
)

effects_mat2$upper <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Upper,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Upper)
)

effects_mat2$estimate <- case_when(
  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Estimate,
  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Estimate)
)

>>>>

effects_mat2$lower <- case_when(
  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Lower,
  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Lower)
)

effects_mat2$upper <- case_when(
  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Upper,
  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Upper)
)

effects_mat2$estimate <- case_when(
  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Estimate,
  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Estimate)
)
